\begin{spell}{Animal Friendship}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a morsel of food)}
	\spDuration{24 hours}
}
This spell lets you convince a beast that you mean it no harm. Choose a beast that you can see within range. It must see and hear you. If the beast’s Intelligence is 4 or higher, the spell fails. Otherwise, the beast must succeed on a Wisdom saving throw or be charmed by you for the spell’s duration. If you or one of your companions harms the target, the spell ends.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can affect one additional beast for each slot level above 1st.
Spell Lists. Bard, Druid, Ranger

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can affect one additional beast for each slot level above 1st.
\end{spell}

\begin{spell}{Bane}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a drop of blood)}
	\spDuration{Concentration, up to 1 minute}
}
Up to three creatures of your choice that you can see within range must make Charisma saving throws. Whenever a target that fails this saving throw makes an attack roll or a saving throw before the spell ends, the target must roll a d4 and subtract the number rolled from the attack roll or saving throw.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
Spell Lists. Bard, Cleric

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
\end{spell}

\begin{spell}{Charm Person}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S}
	\spDuration{1 hour}
}
You attempt to charm a humanoid you can see within range. It must make a Wisdom saving throw, and does so with advantage if you or your companions are fighting it. If it fails the saving throw, it is charmed by you until the spell ends or until you or your companions do anything harmful to it. The charmed creature regards you as a friendly acquaintance. When the spell ends, the creature knows it was charmed by you.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st. The creatures must be within 30 feet of each other when you target them.
Spell Lists. Bard, Druid, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st. The creatures must be within 30 feet of each other when you target them.
\end{spell}

\begin{spell}{Color Spray}{PHB}{1st-level illusion}
{
	\spTime{1 action}
	\spRange{Self (15-foot cone)}
	\spComponents{V, S, M (a pinch of powder or sand that is colored red, yellow, and blue)}
	\spDuration{1 round}
}
A dazzling array of flashing, colored light springs from your hand. Roll 6d10, the total is how many hit points of creatures this spell can effect. Creatures in a 15-foot cone originating from you are affected in ascending order of their current hit points (ignoring unconscious creatures and creatures that can’t see).
Starting with the creature that has the lowest current hit points, each creature affected by this spell is blinded until the end of your next turn. Subtract each creature’s hit points from the total before moving on to the creature with the next lowest hit points. A creature’s hit points must be equal to or less than the remaining total for the creature to be affected.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, roll an additional 2d10 for each slot level above 1st.
Spell Lists. Bard (Optional), Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, roll an additional 2d10 for each slot level above 1st.
\end{spell}

\begin{spell}{Command}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{1 round}
}
You speak a one-word command to a creature you can see within range. The target must succeed on a Wisdom saving throw or follow the command on its next turn. The spell has no effect if the target is undead, if it doesn’t understand your language, or if your command is directly harmful to it. Some typical commands and their effects follow. You might issue a command other than one described here. If you do so, the DM determines how the target behaves. If the target can’t follow your command, the spell ends.
Approach. The target moves toward you by the shortest and most direct route, ending its turn if it moves within 5 feet of you.
Drop. The target drops whatever it is holding and then ends its turn.
Flee. The target spends its turn moving away from you by the fastest available means.
Grovel. The target falls prone and then ends its turn.
Halt. The target doesn’t move and takes no actions. A flying creature stays aloft, provided that it is able to do so. If it must move to stay aloft, it flies the minimum distance needed to remain in the air.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can affect one additional creature for each slot level above 1st. The creatures must be within 30 feet of each other when you target them.
Spell Lists. Bard (Optional), Cleric, Paladin

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can affect one additional creature for each slot level above 1st. The creatures must be within 30 feet of each other when you target them.
\end{spell}

\begin{spell}{Comprehend Languages}{PHB}{1st-level divination (ritual)}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a pinch of soot and salt)}
	\spDuration{1 hour}
}
For the duration, you understand the literal meaning of any spoken language that you hear. You also understand any written language that you see, but you must be touching the surface on which the words are written. It takes about 1 minute to read one page of text.
This spell doesn’t decode secret messages in a text or glyph, such as an arcane sigil, that isn’t part of a written language.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Cure Wounds}{PHB}{1st-level evocation}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
A creature you touch regains a number of hit points equal to 1d8 + your spellcasting ability modifier. This spell has no effect on undead or constructs.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, the healing increases by 1d8 for each slot level above 1st.
Spell Lists. Artificer, Bard, Cleric, Druid, Paladin, Ranger

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, the healing increases by 1d8 for each slot level above 1st.
\end{spell}

\begin{spell}{Detect Magic}{PHB}{1st-level divination (ritual)}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{Concentration, up to 10 minutes}
}
For the duration, you sense the presence of magic within 30 feet of you. If you sense magic in this way, you can use your action to see a faint aura around any visible creature or object in the area that bears magic, and you learn its school of magic, if any.
The spell can penetrate most barriers, but is blocked by 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt.
Spell Lists. Artificer, Bard, Cleric, Druid, Paladin, Ranger, Sorcerer, Wizard
\end{spell}

\begin{spell}{Disguise Self}{PHB}{1st-level illusion}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{1 hour}
}
You make yourself – including your clothing, armor, weapons, and other belongings on your person – look different until the spell ends or until you use your action to dismiss it. You can seem 1 foot shorter or taller and can appear thin, fat, or in between. You can’t change your body type, so you must adopt a form that has the same basic arrangement of limbs. Otherwise, the extent of the illusion is up to you.
The changes wrought by this spell fail to hold up to physical inspection. For example, if you use this spell to add a hat to your outfit, objects pass through the hat, and anyone who touches it would feel nothing or would feel your head and hair. If you use this spell to appear thinner than you are, the hand of someone who reaches out to touch you would bump into you while it was seemingly still in midair. To discern that you are disguised, a creature can use its action to inspect your appearance and must succeed on an Intelligence (Investigation) check against your spell save DC.
Spell Lists. Artificer, Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Dissonant Whispers}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
You whisper a discordant melody that only one creature of your choice within range can hear, wracking it with terrible pain. The target must make a Wisdom saving throw. On a failed save, it takes 3d6 psychic damage and must immediately use its reaction, if available, to move as far as its speed allows away from you. The creature doesn’t move into obviously dangerous ground, such as a fire or a pit. On a successful save, the target takes half as much damage and doesn’t have to move away. A deafened creature automatically succeeds on the save.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d6 for each slot level above 1st.
Spell Lists. Bard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d6 for each slot level above 1st.
\end{spell}

\begin{spell}{Distort Value}{A Inc.}{1st-level Illusion}
{
	\spTime{1 minute}
	\spRange{Touch}
	\spComponents{V}
	\spDuration{8 hours}
}
You cast this spell on an object no more than 1 foot on a side, doubling the object's perceived value by adding illusionary flourish or reducing its perceived value by half with the help of illusionary dents and scratches. Anyone examining the object must roll an Investigation check against your spell DC.
At Higher Levels. When you cast this spell using a higher spell slot, you increase the size of the object by 1 foot per spell slot over 1st.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a higher spell slot, you increase the size of the object by 1 foot per spell slot over 1st.
\end{spell}

\begin{spell}{Earth Tremor}{XGE/EEPC}{1st-level evocation}
{
	\spTime{1 action}
	\spRange{Self (10-foot radius)}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
You cause a tremor in the ground in a 10-foot radius. Each creature other than you in that area must make a Dexterity saving throw. On a failed save, a creature takes 1d6 bludgeoning damage and is knocked prone. If the ground in that area is loose earth or stone, it becomes difficult terrain until cleared.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d6 for each slot level above 1st.
Spell Lists. Bard, Druid, Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d6 for each slot level above 1st.
\end{spell}

\begin{spell}{Faerie Fire}{PHB}{1st-level evocation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Concentration, up to 1 minute}
}
Each object in a 20-foot cube within range is outlined in blue, green, or violet light (your choice).
Any creature in the area when the spell is cast is also outlined in light if it fails a Dexterity saving throw. For the duration, objects and affected creatures shed dim light in a 10-foot radius.
Any attack roll against an affected creature or object has advantage if the attacker can see it, and the affected creature or object can’t benefit from being invisible.
Spell Lists. Artificer, Bard, Druid
\end{spell}

\begin{spell}{Feather Fall}{PHB}{1st-level transmutation}
{
	\spTime{1 reaction, which you take when you or a creature within 60 feet of you falls}
	\spRange{60 feet}
	\spComponents{V, M (a small feather or piece of down)}
	\spDuration{1 minute}
}
Choose up to five falling creatures within range. A falling creature’s rate of descent slows to 60 feet per round until the spell ends. If the creature lands before the spell ends, it takes no falling damage and can land on its feet, and the spell ends for that creature.
Spell Lists. Artificer, Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Guiding Hand (UA)}{UA-36}{1st-level divination (ritual)}
{
	\spTime{1 minute}
	\spRange{5 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 8 hours}
}
You create a Tiny incorporeal hand of shimmering light in an unoccupied space you can see within range. The hand exists for the duration, but it disappears if you teleport or you travel to a different plane of existence.
When the hand appears, you name one major landmark, such as a city, mountain, castle, or battlefield on the same plane of existence as you. Someone in history must have visited the site and mapped it. If the landmark appears on no map in existence, the spell fails. Otherwise, whenever you move toward the hand, it moves away from you at the same speed you moved, and it moves in the direction of the landmark, always remaining 5 feet away from you.
If you don’t move toward the hand, it remains in place until you do and beckons for you to follow once every 1d4 minutes.
Spell Lists. Bard, Cleric, Druid, Wizard
\end{spell}

\begin{spell}{Healing Word}{PHB}{1st-level evocation}
{
	\spTime{1 bonus action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
A creature of your choice that you can see within range regains hit points equal to 1d4 + your spellcasting ability modifier. This spell has no effect on undead or constructs.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, the healing increases by 1d4 for each slot level above 1st.
Spell Lists. Bard, Cleric, Druid

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, the healing increases by 1d4 for each slot level above 1st.
\end{spell}

\begin{spell}{Heroism}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
A willing creature you touch is imbued with bravery. Until the spell ends, the creature is immune to being frightened and gains temporary hit points equal to your spellcasting ability modifier at the start of each of its turns. When the spell ends, the target loses any remaining temporary hit points from this spell.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
Spell Lists. Bard, Paladin

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
\end{spell}

\begin{spell}{Identify}{PHB}{1st-level divination (ritual)}
{
	\spTime{1 minute}
	\spRange{Touch}
	\spComponents{V, S, M (a pearl worth at least 100 gp and an owl feather)}
	\spDuration{Instantaneous}
}
You choose one object that you must touch throughout the casting of the spell. If it is a magic item or some other magic-imbued object, you learn its properties and how to use them, whether it requires attunement to use, and how many charges it has, if any. You learn whether any spells are affecting the item and what they are. If the item was created by a spell, you learn which spell created it.
If you instead touch a creature throughout the casting, you learn what spells, if any, are currently affecting it.
Spell Lists. Artificer, Bard, Wizard
\end{spell}

\begin{spell}{Illusory Script}{PHB}{1st-level illusion (ritual)}
{
	\spTime{1 minute}
	\spRange{Touch}
	\spComponents{S, M (a lead-based ink worth at least 10 gp, which the spell consumes)}
	\spDuration{10 days}
}
You write on parchment, paper, or some other suitable writing material and imbue it with a potent illusion that lasts for the duration.
To you and any creatures you designate when you cast the spell, the writing appears normal, written in your hand, and conveys whatever meaning you intended when you wrote the text. To all others, the writing appears as if it were written in an unknown or magical script that is unintelligible. Alternatively, you can cause the writing to appear to be an entirely different message, written in a different hand and language, though the language must be one you know.
Should the spell be dispelled, the original script and the illusion both disappear. A creature with truesight can read the hidden message.
Spell Lists. Bard, Warlock, Wizard
\end{spell}

\begin{spell}{Longstrider}{PHB}{1st-level transmutation}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S, M (a pinch of dirt)}
	\spDuration{1 hour}
}
You touch a creature. The target’s speed increases by 10 feet until the spell ends.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
Spell Lists. Artificer, Bard, Druid, Ranger, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, you can target one additional creature for each slot level above 1st.
\end{spell}

\begin{spell}{Puppet (UA)}{UA-36}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
Your gesture forces one humanoid you can see within range to make a Constitution saving throw. On a failed save, the target must move up to its speed in a direction you choose. In addition, you can cause the target to drop whatever it is holding. This spell has no effect on a humanoid that is immune to being charmed.
Spell Lists. Bard, Warlock, Wizard
HBThis spell is somewhat overpowered. Forced movement is one thing, but forced disarmament is very strong. I would recommend allowing only forced movement or forced disarmament, not both.
\end{spell}

\begin{spell}{Sense Emotion (UA)}{UA-36}{1st-level divination}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
You attune your senses to pick up the emotions of others for the duration. When you cast the spell, and as your action on each turn until the spell ends, you can focus your senses on one humanoid you can see within 30 feet of you. You instantly learn the target’s prevailing emotion, whether it’s love, anger, pain, fear, calm, or something else. If the target isn’t actually humanoid or it is immune to being charmed, you sense that it is calm.
Spell Lists. Bard, Warlock, Wizard
\end{spell}

\begin{spell}{Silent Image}{PHB}{1st-level illusion}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a bit of fleece)}
	\spDuration{Concentration, up to 10 minutes}
}
You create the image of an object, a creature, or some other visible phenomenon that is no larger than a 15-foot cube. The image appears at a spot within range and lasts for the duration. The image is purely visual; it isn’t accompanied by sound, smell, or other sensory effects.
You can use your action to cause the image to move to any spot within range. As the image changes location, you can alter its appearance so that its movements appear natural for the image. For example, if you create an image of a creature and move it, you can alter the image so that it appears to be walking.
Physical interaction with the image reveals it to be an illusion, because things can pass through it. A creature that uses its action to examine the image can determine that it is an illusion with a successful Intelligence (Investigation) check against your spell save DC. If a creature discerns the illusion for what it is, the creature can see through the image.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Silvery Barbs}{S:ACC}{1st-level Enchantment}
{
	\spTime{1 reaction, which you take when a creature you can see within 60 feet of yourself succeeds on an attack roll, an ability check, or a saving throw}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
You magically distract the triggering creature and turn its momentary uncertainty into encouragement for another creature. The triggering creature must reroll the d20 and use the lower roll.
You can then choose a different creature you can see within range (you can choose yourself). The chosen creature has advantage on the next attack roll, ability check, or saving throw it makes within 1 minute. A creature can be empowered by only one use of this spell at a time.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Sleep}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{90 feet}
	\spComponents{V, S, M (a pinch of fine sand, rose petals, or a cricket)}
	\spDuration{1 minute}
}
This spell sends creatures into a magical slumber. Roll 5d8, the total is how many hit points of creatures this spell can affect. Creatures within 20 feet of a point you choose within range are affected in ascending order of their current hit points (ignoring unconscious creatures).
Starting with the creature that has the lowest current hit points, each creature affected by this spell falls unconscious until the spell ends, the sleeper takes damage, or someone uses an action to shake or slap the sleeper awake. Subtract each creature’s hit points from the total before moving on to the creature with the next lowest hit points. A creature’s hit points must be equal to or less than the remaining total for that creature to be affected. Undead and creatures immune to being charmed aren’t affected by this spell.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, roll an additional 2d8 for each slot level above 1st.
Spell Lists. Bard, Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, roll an additional 2d8 for each slot level above 1st.
\end{spell}

\begin{spell}{Speak with Animals}{PHB}{1st-level divination (ritual)}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{10 minutes}
}
You gain the ability to comprehend and verbally communicate with beasts for the duration. The knowledge and awareness of many beasts is limited by their intelligence, but at minimum, beasts can give you information about nearby locations and monsters, including whatever they can perceive or have perceived within the past day. You might be able to persuade a beast to perform a small favor for you, at the DM’s discretion.
Spell Lists. Bard, Druid, Ranger
\end{spell}

\begin{spell}{Sudden Awakening (UA)}{UA-36}{1st-level enchantment}
{
	\spTime{1 bonus action}
	\spRange{10 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
Each sleeping creature you choose within range awakens, and then each prone creature within range can stand up without expending any movement.
Spell Lists. Bard, Ranger, Sorcerer, Wizard
\end{spell}

\begin{spell}{Tasha's Hideous Laughter}{PHB}{1st-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (tiny tarts and a feather that is waved in the air)}
	\spDuration{Concentration, up to 1 minute}
}
A creature of your choice that you can see within range perceives everything as hilariously funny and falls into fits of laughter if this spell affects it. The target must succeed on a Wisdom saving throw or fall prone, becoming incapacitated and unable to stand up for the duration. A creature with an Intelligence score of 4 or less isn’t affected.
At the end of each of its turns, and each time it takes damage, the target can make another Wisdom saving throw. The target has advantage on the saving throw if it’s triggered by damage. On a success, the spell ends.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{Thunderwave}{PHB}{1st-level evocation}
{
	\spTime{1 action}
	\spRange{Self (15-foot cube)}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
A wave of thunderous force sweeps out from you. Each creature in a 15-foot cube originating from you must make a Constitution saving throw. On a failed save, a creature takes 2d8 thunder damage and is pushed 10 feet away from you. On a successful save, the creature takes half as much damage and isn’t pushed.
In addition, unsecured objects that are completely within the area of effect are automatically pushed 10 feet away from you by the spell’s effect, and the spell emits a thunderous boom audible out to 300 feet.
At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d8 for each slot level above 1st.
Spell Lists. Bard, Druid, Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 2nd level or higher, the damage increases by 1d8 for each slot level above 1st.
\end{spell}

\begin{spell}{Unearthly Chorus (UA)}{UA-36}{1st-level illusion}
{
	\spTime{1 action}
	\spRange{Self (30-foot radius)}
	\spComponents{V}
	\spDuration{Concentration, up to 10 minutes}
}
Music of a style you choose fills the air around you in a 30-foot radius. The music spreads around corners and can be heard from up to 100 feet away. The music moves with you, centered on you for the duration.
Until the spell ends, you make Charisma (Performance) checks with advantage. In addition, you can use a bonus action on each of your turns to beguile one creature you choose within 30 feet of you that can see you and hear the music. The creature must make a Charisma saving throw. If you or your companions are attacking it, the creature automatically succeeds on the saving throw. On a failure, the creature becomes friendly to you for as long as it can hear the music and for 1 hour thereafter. You make Charisma (Deception) checks and Charisma (Persuasion) checks against creatures made friendly by this spell with advantage.
Spell Lists. Bard
\end{spell}

\begin{spell}{Unseen Servant}{PHB}{1st-level conjuration (ritual)}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a piece of string and a bit of wood)}
	\spDuration{1 hour}
}
This spell creates an invisible, mindless, shapeless, Medium force that performs simple tasks at your command until the spell ends. The servant springs into existence in an unoccupied space on the ground within range. It has AC 10, 1 hit point, and a Strength of 2, and it can’t attack. If it drops to 0 hit points, the spell ends.
Once on each of your turns as a bonus action, you can mentally command the servant to move up to 15 feet and interact with an object. The servant can perform simple tasks that a human servant could do, such as fetching things, cleaning, mending, folding clothes, lighting fires, serving food, and pouring wine. Once you give the command, the servant performs the task to the best of its ability until it completes the task, then waits for your next command.
If you command the servant to perform a task that would move it more than 60 feet away from you, the spell ends.
Spell Lists. Bard, Warlock, Wizard
\end{spell}

