\begin{spell}{Aid}{PHB}{2nd-level abjuration}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a tiny strip of white cloth)}
	\spDuration{8 hours}
}
Your spell bolsters your allies with toughness and resolve. Choose up to three creatures within range. Each target’s hit point maximum and current hit points increase by 5 for the duration.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, a target’s hit points increase by an additional 5 for each slot level above 2nd.
Spell Lists. Artificer, Bard (Optional), Cleric, Paladin, Ranger (Optional)

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, a target’s hit points increase by an additional 5 for each slot level above 2nd.
\end{spell}

\begin{spell}{Animal Messenger}{PHB}{2nd-level enchantment (ritual)}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a morsel of food)}
	\spDuration{24 hours}
}
By means of this spell, you use an animal to deliver a message. Choose a Tiny beast you can see within range, such as a squirrel, a blue jay, or a bat. You specify a location, which you must have visited, and a recipient who matches a general description, such as “a man or woman dressed in the uniform of the town guard” or “a red-haired dwarf wearing a pointed hat.” You also speak a message of up to twenty-five words. The target beast travels for the duration of the spell toward the specified location, covering about 50 miles per 24 hours for a flying messenger, or 25 miles for other animals.
When the messenger arrives, it delivers your message to the creature that you described, replicating the sound of your voice. The messenger speaks only to a creature matching the description you gave. If the messenger doesn’t reach its destination before the spell ends, the message is lost, and the beast makes its way back to where you cast this spell.
At Higher Levels. If you cast this spell using a spell slot of 3rd level or higher, the duration of the spell increases by 48 hours for each slot level above 2nd.
Spell Lists. Bard, Druid, Ranger

\note{At Higher Levels.} If you cast this spell using a spell slot of 3rd level or higher, the duration of the spell increases by 48 hours for each slot level above 2nd.
\end{spell}

\begin{spell}{Blindness/Deafness}{PHB}{2nd-level necromancy}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V}
	\spDuration{1 minute}
}
You can blind or deafen a foe. Choose one creature that you can see within range to make a Constitution saving throw. If it fails, the target is either blinded or deafened (your choice) for the duration. At the end of each of its turns, the target can make a Constitution saving throw. On a success, the spell ends.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
Spell Lists. Bard, Cleric, Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
\end{spell}

\begin{spell}{Borrowed Knowledge}{S:ACC}{2nd-level Divination}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a book worth at least 25 gp)}
	\spDuration{1 hour}
}
You draw on knowledge from spirits of the past. Choose one skill in which you lack proficiency. For the spell's duration, you have proficiency in the chosen skill. The spell ends early if you cast it again.
Spell Lists. Bard, Cleric, Warlock, Wizard
\end{spell}

\begin{spell}{Calm Emotions}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
You attempt to suppress strong emotions in a group of people. Each humanoid in a 20-foot-radius sphere centered on a point you choose within range must make a Charisma saving throw; a creature can choose to fail this saving throw if it wishes. If a creature fails its saving throw, choose one of the following two effects. You can suppress any effect causing a target to be charmed or frightened. When this spell ends, any suppressed effect resumes, provided that its duration has not expired in the meantime.
Alternatively, you can make a target indifferent about creatures of your choice that it is hostile toward. This indifference ends if the target is attacked or harmed by a spell or if it witnesses any of its friends being harmed. When the spell ends, the creature becomes hostile again, unless the DM rules otherwise.
Spell Lists. Bard, Cleric
\end{spell}

\begin{spell}{Cloud of Daggers}{PHB}{2nd-level conjuration}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a sliver of glass)}
	\spDuration{Concentration, up to 1 minute}
}
You fill the air with spinning daggers in a cube 5 feet on each side, centered on a point you choose within range. A creature takes 4d4 slashing damage when it enters the spell’s area for the first time on a turn or starts its turn there.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 2d4 for each slot level above 2nd.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 2d4 for each slot level above 2nd.
\end{spell}

\begin{spell}{Crown of Madness}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
One humanoid of your choice that you can see within range must succeed on a Wisdom saving throw or become charmed by you for the duration. While the target is charmed in this way, a twisted crown of jagged iron appears on its head, and a madness glows in its eyes.
The charmed target must use its action before moving on each of its turns to make a melee attack against a creature other than itself that you mentally choose. The target can act normally on its turn if you choose no creature or if none are within its reach.
On your subsequent turns, you must use your action to maintain control over the target, or the spell ends. Also, the target can make a Wisdom saving throw at the end of each of its turns. On a success, the spell ends.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Detect Thoughts}{PHB}{2nd-level divination}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a copper piece)}
	\spDuration{Concentration, up to 1 minute}
}
For the duration, you can read the thoughts of certain creatures. When you cast the spell and as your action on each turn until the spell ends, you can focus your mind on any one creature that you can see within 30 feet of you. If the creature you choose has an Intelligence of 3 or lower or doesn’t speak any language, the creature is unaffected.
You initially learn the surface thoughts of the creature - what is most on its mind in that moment. As an action, you can either shift your attention to another creature’s thoughts or attempt to probe deeper into the same creature’s mind. If you probe deeper, the target must make a Wisdom saving throw. If it fails, you gain insight into its reasoning (if any), its emotional state, and something that looms large in its mind (such as something it worries over, loves, or hates). If it succeeds, the spell ends. Either way, the target knows that you are probing into its mind, and unless you shift your attention to another creature’s thoughts, the creature can use its action on its turn to make an Intelligence check contested by your Intelligence check; if it succeeds, the spell ends.
Questions verbally directed at the target creature naturally shape the course of its thoughts, so this spell is particularly effective as part of an interrogation.
You can also use this spell to detect the presence of thinking creatures you can’t see. When you cast the spell or as your action during the duration, you can search for thoughts within 30 feet of you. The spell can penetrate barriers, but 2 feet of rock, 2 inches of any metal other than lead, or a thin sheet of lead blocks you. You can’t detect a creature with an Intelligence of 3 or lower or one that doesn’t speak any language.
Once you detect the presence of a creature in this way, you can read its thoughts for the rest of the duration as described above, even if you can’t see it, but it must still be within range.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Enhance Ability}{PHB}{2nd-level transmutation}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S, M (fur or a feather from a beast)}
	\spDuration{Concentration, up to 1 hour}
}
You touch a creature and bestow upon it a magical enhancement. Choose one of the following effects; the target gains the effect until the spell ends.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
Spell Lists. Artificer, Bard, Cleric, Druid, Ranger (Optional), Sorcerer, Wizard (Optional)

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
\end{spell}

\begin{spell}{Enlarge/Reduce}{PHB}{2nd-level transmutation}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a pinch of powdered iron)}
	\spDuration{Concentration, up to 1 minute}
}
You cause a creature or an object you can see within range to grow larger or smaller for the duration. Choose either a creature or an object that is neither worn nor carried. If the target is unwilling, it can make a Constitution saving throw. On a success, the spell has no effect.
If the target is a creature, everything it is wearing and carrying changes size with it. Any item dropped by an affected creature returns to normal size at once.
Enlarge. The target’s size doubles in all dimensions, and its weight is multiplied by eight. This growth increases its size by one category – from Medium to Large, for example. If there isn’t enough room for the target to double its size, the creature or object attains the maximum possible size in the space available. Until the spell ends, the target also has advantage on Strength checks and Strength saving throws. The target’s weapons also grow to match its new size. While these weapons are enlarged, the target’s attack with them deal 1d4 extra damage.
Reduce. The target’s size is halved in all dimensions, and its weight is reduced to one-eighth of normal. This reduction decreases its size by one category – from Medium to Small, for example. Until the spell ends, the target also has disadvantage on Strength checks and Strength saving throws. The target’s weapons also shrink to match its new size. While these weapons are reduced, the target’s attacks with them deal 1d4 less damage (this can’t reduce the damage below 1).
Spell Lists. Artificer, Bard (Optional), Druid (Optional), Sorcerer, Wizard
\end{spell}

\begin{spell}{Enthrall}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{1 minute}
}
You weave a distracting string of words, causing creatures of your choice that you can see within range and that can hear you to make a Wisdom saving throw. Any creature that can’t be charmed succeeds on this saving throw automatically, and if you or your companions are fighting a creature, it has advantage on the save. On a failed save, the target has disadvantage on Wisdom (Perception) checks made to perceive any creature other than you until the spell ends or until the target can no longer hear you. The spell ends if you are incapacitated or can no longer speak.
Spell Lists. Bard, Warlock
\end{spell}

\begin{spell}{Gift of Gab}{A Inc.}{2nd-level enchantment}
{
	\spTime{1 reaction, which you take when you speak to another creature}
	\spRange{Self}
	\spComponents{V, S, M (2 gold coins, which is consumed as tax for using the spell)}
	\spDuration{Instantaneous}
}
When you cast this spell, you skillfully reshape the memories of listeners in your immediate area, so that each creature of your choice within 5 feet of you forgets everything you said within the last 6 seconds. Those creatures then remember that you actually said the words you speak as the verbal component of the spell.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{Heat Metal}{PHB}{2nd-level transmutation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a piece of iron and a flame)}
	\spDuration{Concentration, up to 1 minute}
}
Choose a manufactured metal object, such as a metal weapon or a suit of heavy or medium metal armor, that you can see within range. You cause the object to glow red-hot. Any creature in physical contact with the object takes 2d8 fire damage when you cast the spell. Until the spell ends, you can use a bonus action on each of your subsequent turns to cause this damage again.
If a creature is holding or wearing the object and takes the damage from it, the creature must succeed on a Constitution saving throw or drop the object if it can. If it doesn’t drop the object, it has disadvantage on attack rolls and ability checks until the start of your next turn.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d8 for each slot level above 2nd.
Spell Lists. Artificer, Bard, Druid

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d8 for each slot level above 2nd.
\end{spell}

\begin{spell}{Hold Person}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a small, straight piece of iron)}
	\spDuration{Concentration, up to 1 minute}
}
Choose a humanoid that you can see within range. The target must succeed on a Wisdom saving throw or be paralyzed for the duration. At the end of each of its turns, the target can make another Wisdom saving throw. On a success, the spell ends on the target.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, you can target one additional humanoid for each slot level above 2nd. The humanoids must be within 30 feet of each other when you target them.
Spell Lists. Bard, Cleric, Druid, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, you can target one additional humanoid for each slot level above 2nd. The humanoids must be within 30 feet of each other when you target them.
\end{spell}

\begin{spell}{Invisibility}{PHB}{2nd-level illusion}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S, M (an eyelash encased in gum arabic)}
	\spDuration{Concentration, up to 1 hour}
}
A creature you touch becomes invisible until the spell ends. Anything the target is wearing or carrying is invisible as long as it is on the target’s person. The spell ends for a target that attacks or casts a spell.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
Spell Lists. Artificer, Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, you can target one additional creature for each slot level above 2nd.
\end{spell}

\begin{spell}{Kinetic Jaunt}{S:ACC}{2nd-level Transmutation}
{
	\spTime{1 bonus action}
	\spRange{Self}
	\spComponents{S}
	\spDuration{Concentration, up to 1 minute}
}
You magically empower your movement with dancelike steps, giving yourself the following benefits for the duration:
Spell Lists. Artificer, Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Knock}{PHB}{2nd-level transmutation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
Choose an object that you can see within range. The object can be a door, a box, a chest, a set of manacles, a padlock, or another object that contains a mundane or magical means that prevents access.
A target that is held shut by a mundane lock or that is stuck or barred becomes unlocked, unstuck, or unbarred. If the object has multiple locks, only one of them is unlocked.
If you choose a target that is held shut with Arcane Lock, that spell is suppressed for 10 minutes, during which time the target can be opened and shut normally.
When you cast the spell, a loud knock, audible from as far away as 300 feet, emanates from the target object.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Lesser Restoration}{PHB}{2nd-level abjuration}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
You touch a creature and can end either one disease or one condition afflicting it. The condition can be blinded, deafened, paralyzed, or poisoned.
Spell Lists. Artificer, Bard, Cleric, Druid, Paladin, Ranger
\end{spell}

\begin{spell}{Locate Animals or Plants}{PHB}{2nd-level divination (ritual)}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a bit of fur from a bloodhound)}
	\spDuration{Instantaneous}
}
Describe or name a specific kind of beast or plant. Concentrating on the voice of nature in your surroundings, you learn the direction and distance to the closest creature or plant of that kind within 5 miles, if any are present.
Spell Lists. Bard, Druid, Ranger
\end{spell}

\begin{spell}{Locate Object}{PHB}{2nd-level divination}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a forked twig)}
	\spDuration{Concentration, up to 10 minutes}
}
Describe or name an object that is familiar to you. You sense the direction to the object’s location, as long as that object is within 1,000 feet of you. If the object is in motion, you know the direction of its movement.
The spell can locate a specific object known to you, as long as you have seen it up close – within 30 feet – at least once. Alternatively, the spell can locate the nearest object of a particular kind, such as a certain kind of apparel, jewelry, furniture, tool, or weapon.
This spell can’t locate an object if any thickness of lead, even a thin sheet, blocks a direct path between you and the object.
Spell Lists. Bard, Cleric, Druid, Paladin, Ranger, Wizard
\end{spell}

\begin{spell}{Magic Mouth}{PHB}{2nd-level illusion (ritual)}
{
	\spTime{1 minute}
	\spRange{30 feet}
	\spComponents{V, S, M (a small bit of honeycomb and jade dust worth at least 10 gp, which the spell consumes)}
	\spDuration{Until dispelled}
}
You implant a message within an object in range, a message that is uttered when a trigger condition is met. Choose an object that you can see and that isn’t being worn or carried by another creature. Then speak the message, which must be 25 words or less, though it can be delivered over as long as 10 minutes. Finally, determine the circumstance that will trigger the spell to deliver your message.
When that circumstance occurs, a magical mouth appears on the object and recites the message in your voice and at the same volume you spoke. If the object you chose has a mouth or something that looks like a mouth (for example, the mouth of a statue), the magical mouth appears there so that words appear to come from the object’s mouth. When you cast this spell, you can have the spell end after it delivers its message, or it can remain and repeats its message whenever the trigger occurs.
The triggering circumstance can be as general or as detailed as you like, though it must be based on visual or audible conditions that occur within 30 feet of the object. For example, you could instruct the mouth to speak when any creature moves within 30 feet of the object or when a silver bell rings within 30 feet of it.
Spell Lists. Artificer, Bard, Wizard
\end{spell}

\begin{spell}{Mirror Image}{PHB}{2nd-level illusion}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{1 minute}
}
Three illusory duplicates of yourself appear in your space. Until the spell ends, the duplicates move with you and mimic your actions, shifting position so it’s impossible to track which image is real. You can use your action to dismiss the illusory duplicates.
Each time a creature targets you with an attack during the spell’s duration, roll a d20 to determine whether the attack instead targets one of your duplicates.
If you have three duplicates, you must roll a 6 or higher to change the attack’s target to a duplicate. With two duplicates, you must roll an 8 or higher. With one duplicate, you must roll an 11 or higher.
A duplicate’s AC equals 10 + your Dexterity modifier. If an attack hits a duplicate, the duplicate is destroyed. A duplicate can be destroyed only by an attack that hits it. It ignores all other damage and effects. The spell ends when all three duplicates are destroyed.
A creature is unaffected by this spell if it can’t see, if it relies on senses other than sight, such as blindsight, or if it can perceive illusions as false, as with truesight.
Spell Lists. Bard (Optional), Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Nathair's Mischief}{FTD}{2nd-level Illusion}
{
	\spTime{1 Action}
	\spRange{60ft}
	\spComponents{S, M (a piece of crust from an apple pie)}
	\spDuration{Concentration, up to 1 minute}
}
You fill a 20-foot cube you can see within range with fey and draconic magic. Roll on the Mischievous Surge table to determine the magical effect produced, and roll again at the start of each of your turns until the spell ends. You can move the cube up to 10 feet before you roll.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Nathair's Mischief (UA)}{UA-78}{2nd-level illusion}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{S, M (a piece of crust from an apple pie)}
	\spDuration{Concentration, up to 1 minute}
}
You fill a 20-foot cube centered on a point you choose within range with fey and draconic magic. Roll on the Mischievous Surge table to determine the magical effect produced. At the start of each of your turns, you can move the cube up to 10 feet and reroll on the table.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Phantasmal Force}{PHB}{2nd-level illusion}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a bit of fleece)}
	\spDuration{Concentration, up to 1 minute}
}
You craft an illusion that takes root in the mind of a creature that you can see within range. The target must make an Intelligence saving throw. On a failed save, you create a phantasmal object, creature, or other visible phenomenon of your choice that is no larger than a 10-foot cube and that is perceivable only to the target for the duration. This spell has no effect on undead or constructs.
The phantasm includes sound, temperature, and other stimuli, also evident only to the creature.
The target can use its action to examine the phantasm with an Intelligence (Investigation) check against your spell save DC. If the check succeeds, the target realizes that the phantasm is an illusion, and the spell ends.
While a target is affected by the spell, the target treats the phantasm as if it were real. The target rationalizes any illogical outcomes from interacting with the phantasm. For example, a target attempting to walk across a phantasmal bridge that spans a chasm falls once it steps onto the bridge. If the target survives the fall, it still believes that the bridge exists and comes up with some other explanation for its fall; it was pushed, it slipped, or a strong wind might have knocked it off.
An affected target is so convinced of the phantasm’s reality that it can even take damage from the illusion. A phantasm created to appear as a creature can attack the target. Similarly, a phantasm created to appear as fire, a pool of acid, or lava can burn the target. Each round on your turn, the phantasm can deal 1d6 psychic damage to the target if it is in the phantasm’s area or within 5 feet of the phantasm, provided that the illusion is of a creature or hazard that could logically deal damage, such as by attacking. The target perceives the damage as a type appropriate to the illusion.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Pyrotechnics}{XGE}{2nd-level transmutation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
Choose an area of flame that you can see and that can fit within a 5-foot cube within range. You can extinguish the fire in that area, and you create either fireworks or smoke.
Fireworks. The target explodes with a dazzling display of colors. Each creature within 10 feet of the target must succeed on a Constitution saving throw or become blinded until the end of your next turn.
Smoke. Thick black smoke spreads out from the target in a 20-foot radius, moving around corners. The area of the smoke is heavily obscured. The smoke persists for 1 minute or until a strong wind disperses it.
Spell Lists. Bard, Sorcerer, Wizard, Artificer
\end{spell}

\begin{spell}{See Invisibility}{PHB}{2nd-level divination}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S, M (a pinch of talc and a small sprinkling of powdered silver)}
	\spDuration{1 hour}
}
For the duration, you see invisible creatures and objects as if they were visible, and you can see into the Ethereal Plane. Ethereal creatures and objects appear ghostly and translucent.
Spell Lists. Artificer, Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Shatter}{PHB}{2nd-level evocation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S, M (a chip of mica)}
	\spDuration{Instantaneous}
}
A sudden loud ringing noise, painfully intense, erupts from a point of your choice within range. Each creature in a 10-foot-radius sphere centered on that point must make a Constitution saving throw. A creature takes 3d8 thunder damage on a failed save, or half as much damage on a successful one. A creature made of inorganic material such as stone, crystal, or metal has disadvantage on this saving throw.
A nonmagical object that isn’t being worn or carried also takes the damage if it’s in the spell’s area.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d8 for each slot level above 2nd.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d8 for each slot level above 2nd.
\end{spell}

\begin{spell}{Silence}{PHB}{2nd-level illusion (ritual)}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 10 minutes}
}
For the duration, no sound can be created within or pass through a 20-foot-radius sphere centered on a point you choose within range. Any creature or object entirely inside the sphere is immune to thunder damage, and creatures are deafened while entirely inside it. Casting a spell that includes a verbal component is impossible there.
Spell Lists. Bard, Cleric, Ranger
\end{spell}

\begin{spell}{Skywrite}{XGE}{2nd-level transmutation (ritual)}
{
	\spTime{1 action}
	\spRange{Sight}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 day}
}
You cause up to ten words to form in a part of the sky you can see. The words appear to be made of cloud and remain in place for the spell’s duration. The words dissipate when the spell ends. A strong wind can disperse the clouds and end the spell early.
Spell Lists. Bard, Druid, Wizard, Artificer
\end{spell}

\begin{spell}{Spray Of Cards}{TBMT}{2nd-level conjuration}
{
	\spTime{1 action}
	\spRange{Self (15-foot cone)}
	\spComponents{V, S, M (a deck of cards)}
	\spDuration{Instantaneous}
}
You spray a 15-foot cone of spectral cards. Each creature in that area must make a Dexterity saving throw. On a failed save, a creature takes 2d10 force damage and has the blinded condition until the end of its next turn. On a successful save, a creature takes half as much damage only.
At Higher Levels. When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d10 for each slot level above 2nd.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 3rd level or higher, the damage increases by 1d10 for each slot level above 2nd.
\end{spell}

\begin{spell}{Spray of Cards (UA)}{UA-85}{2nd-level conjuration}
{
	\spTime{1 action}
	\spRange{15-foot cone}
	\spComponents{V, S, M (a deck of cards)}
	\spDuration{Instantaneous}
}
You spray spectral cards from your hands or sleeve; the cards blind or slash at your enemies, and then vanish. Choose one of the following effects for the cards:
At Higher Levels. When you cast this spell using a spell slot of 4th level or higher, the damage of cutting cards increases by 1d10 for every two slot levels above 2nd
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 4th level or higher, the damage of cutting cards increases by 1d10 for every two slot levels above 2nd
\end{spell}

\begin{spell}{Suggestion}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, M (a snake’s tongue and either a bit of honeycomb or a drop of sweet oil)}
	\spDuration{Concentration, up to 8 hours}
}
You suggest a course of activity (limited to a sentence or two) and magically influence a creature you can see within range that can hear and understand you. Creatures that can’t be charmed are immune to this effect. The suggestion must be worded in such a manner as to make the course of action sound reasonable. Asking the creature to stab itself, throw itself onto a spear, immolate itself, or do some other obviously harmful act ends the spell.
The target must make a Wisdom saving throw. On a failed save, it purses the course of action you described to the best of its ability. The suggested course of action can continue for the entire duration. If the suggested activity can be completed in a shorter time, the spell ends when the subject finishes what it was asked to do.
You can also specify conditions that will trigger a special activity during the duration. For example, you might suggest that a knight give her warhorse to the first beggar she meets. If the condition isn’t met before the spell expires, the activity isn’t performed.
If you or any of your companions damage the target, the spell ends.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Warding Wind}{XGE}{2nd-level evocation}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V}
	\spDuration{Concentration, up to 10 minutes}
}
A strong wind (20 miles per hour) blows around you in a 10-foot radius and moves with you, remaining centered on you. The wind lasts for the spell’s duration.
The wind has the following effects:
Spell Lists. Bard, Druid, Sorcerer, Wizard
\end{spell}

\begin{spell}{Zone of Truth}{PHB}{2nd-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{10 minutes}
}
You create a magical zone that guards against deception in a 15-foot-radius sphere centered on a point of your choice within range. Until the spell ends, a creature that enters the spell’s area for the first time on a turn or starts its turn there must make a Charisma saving throw. On a failed save, a creature can’t speak a deliberate lie while in the radius. You know whether each creature succeeds or fails on its saving throw.
An affected creature is aware of the spell and can thus avoid answering questions to which it would normally respond with a lie. Such creatures can be evasive in its answers as long as it remains within the boundaries of the truth.
Spell Lists. Bard, Cleric, Paladin
\end{spell}

