\begin{spell}{Animate Objects}{PHB}{5th-level transmutation}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
Objects come to life at your command. Choose up to ten nonmagical objects within range that are not being worn or carried. Medium targets count as two objects, Large targets count as four objects, Huge targets count as eight objects. You can’t animate any object larger than Huge. Each target animates and becomes a creature under your control until the spell ends or until reduced to 0 hit points.
As a bonus action, you can mentally command any creature you made with this spell if the creature is within 500 feet of you (if you control multiple creatures, you can command any or all of them at the same time, issuing the same command to each one). You decide what action the creature will take and where it will move during its next turn, or you can issue a general command, such as to guard a particular chamber or corridor. If you issue no commands, the creature only defends itself against hostile creatures. Once given an order, the creature continues to follow it until its task is complete.
An animated object is a construct with AC, hit points, attacks, Strength, and Dexterity determine by its size. Its Constitution is 10 and its Intelligence and Wisdom are 3, and its Charisma is 1. Its speed is 30 feet; if the objects lack legs or other appendages it can use for locomotion, it instead has a flying speed of 30 feet and can hover. If the object is securely attached to a surface or larger object, such as a chain bolted to a wall, its speed is 0. It has blindsight with a radius of 30 feet and is blind beyond that distance. When the animated object drops to 0 hit points, it reverts to its original object form, and any remaining damage carries over to its original object form.
If you command an object to attack, it can make a single melee attack against a creature within 5 feet of it. It makes a slam attack with an attack bonus and bludgeoning damage determine by its size. The DM might rule that a specific object inflicts slashing or piercing damage based on its form.
At Higher Levels. If you cast this spell using a spell slot of 6th level or higher, you can animate two additional objects for each slot level above 5th.
Spell Lists. Artificer, Bard, Sorcerer, Wizard

\note{At Higher Levels.} If you cast this spell using a spell slot of 6th level or higher, you can animate two additional objects for each slot level above 5th.
\end{spell}

\begin{spell}{Awaken}{PHB}{5th-level transmutation}
{
	\spTime{8 hours}
	\spRange{Touch}
	\spComponents{V, S, M (an agate worth at least 1,000 gp, which the spell consumes)}
	\spDuration{Instantaneous}
}
After spending the casting time tracing magical pathways within a precious gemstone, you touch a huge or smaller beast or plant. The target must have either no Intelligence score or an Intelligence of 3 or less.
The target gains an Intelligence of 10. The target also gains the ability to speak one language you know. If the target is a plant, it gains the ability to move its limbs, roots, vines, creepers, and so forth, and it gains senses similar to a human’s. Your DM chooses statistics appropriate for the awakened plant, such as the statistics for the awakened shrub or the awakened tree.
The awakened beast or plant is charmed by you for 30 days or until you and your companions do anything harmful to it. When the charmed condition ends, the awakened creature chooses whether to remain friendly to you, based on how you treated it while it was charmed.
Spell Lists. Bard, Druid
\end{spell}

\begin{spell}{Dominate Person}{PHB}{5th-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
You attempt to beguile a humanoid that you can see within range. It must succeed on a Wisdom saving throw or be charmed by you for the duration. If you or creatures that are friendly to you are fighting it, it has advantage on the saving throw.
While the target is charmed, you have a telepathic link with it as long as the two of you are on the same plane of existence. You can use this telepathic link to issue commands to the creature while you are conscious (no action required), which it does its best to obey. You can specify a simple and general course of action, such as "Attack that creature", "Run over there", or "Fetch that object". If the creature completes the order and doesn’t receive further direction from you, it defends and preserves itself to the best of its ability.
You can use your action to take total and precise control of the target. Until the end of your next turn, the creature takes only the actions you choose, and doesn’t do anything that you don’t allow it to do. During this time you can also cause the creature to use a reaction, but this requires you to use your own reaction as well.
Each time the target takes damage, it makes a new Wisdom saving throw against the spell. If the saving throw succeeds, the spell ends.
At Higher Levels. When you cast this spell using a 6th-level spell slot, the duration is concentration, up to 10 minutes. When you use a 7th-level spell slot, the duration is concentration, up to 1 hour. When you use a spell slot of 8th level or higher, the duration is concentration, up to 8 hours.
Spell Lists. Bard, Sorcerer, Wizard

\note{At Higher Levels.} When you cast this spell using a 6th-level spell slot, the duration is concentration, up to 10 minutes. When you use a 7th-level spell slot, the duration is concentration, up to 1 hour. When you use a spell slot of 8th level or higher, the duration is concentration, up to 8 hours.
\end{spell}

\begin{spell}{Dream}{PHB}{5th-level illusion}
{
	\spTime{1 minute}
	\spRange{Special}
	\spComponents{V, S, M (a handful of sand, a dab of ink, and a writing quill plucked from a sleeping bird)}
	\spDuration{8 hours}
}
This spell shapes a creature’s dreams. Choose a creature known to you as the target of this spell. The target must be on the same plane of existence as you. Creatures that don’t sleep, such as elves, can’t be contacted by this spell. You, or a willing creature you touch, enters a trance state, acting as a messenger. While in the trance, the messenger is aware of their surroundings, but can’t take actions or move.
If the target is asleep, the messenger appears in the target’s dreams and can converse with the target as long as it remains asleep, through the duration of the spell. The messenger can also shape the environment of the dream, creating landscapes, objects, and other images. The messenger can emerge from the trance at any time, ending the effect of the spell early. The target recalls the dream perfectly upon waking. If the target is awake when you cast the spell, the messenger knows it, and can either end the trance (and the spell) or wait for the target to fall asleep, at which point the messenger appears in the target’s dreams.
You can make the messenger appear monstrous and terrifying to the target. If you do, the messenger can deliver a message of no more than ten words and then the target must make a Wisdom saving throw. On a failed save, echoes of the phantasmal monstrosity spawn a nightmare that lasts the duration of the target’s sleep and prevents the target from gaining any benefit from that rest. In addition, when the target wakes up, it takes 3d6 psychic damage.
If you have a body part, lock of hair, clipping from a nail, or similar portion of the target’s body, the target makes its saving throw with disadvantage.
Spell Lists. Bard, Warlock, Wizard
\end{spell}

\begin{spell}{Geas}{PHB}{5th-level enchantment}
{
	\spTime{1 minute}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{30 days}
}
You place a magical command on a creature that you can see within range, forcing it to carry out some service or refrain from some action or course of activity as you decide.
If the creature can understand you, it must succeed on a Wisdom saving throw or become charmed by you for the duration. While the creature is charmed by you, it takes 5d10 psychic damage each time it acts in a manner directly counter to your instructions, but no more than once each day. A creature that can’t understand you is unaffected by the spell.
You can issue any command you choose, short of an activity that would result in certain death. Should you issue a suicidal command, the spell ends. You can end the spell early by using an action to dismiss it. A Remove Curse, Greater Restoration, or Wish spell also ends it.
At Higher Levels. When you cast this spell using a spell slot of 7th or 8th level, the duration is 1 year. When you cast this spell using a spell slot of 9th level, the spell lasts until it is ended by one of the spells mentioned above.
Spell Lists. Bard, Cleric, Druid, Paladin, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 7th or 8th level, the duration is 1 year. When you cast this spell using a spell slot of 9th level, the spell lasts until it is ended by one of the spells mentioned above.
\end{spell}

\begin{spell}{Greater Restoration}{PHB}{5th-level abjuration}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S, M (diamond dust worth at least 100 gp, which the spell consumes)}
	\spDuration{Instantaneous}
}
You imbue a creature you touch with positive energy to undo a debilitating effect. You can reduce the target’s exhaustion level by one, or end one of the following effects on the target:
Spell Lists. Artificer, Bard, Cleric, Druid, Ranger (Optional)
\end{spell}

\begin{spell}{Hold Monster}{PHB}{5th-level enchantment}
{
	\spTime{1 action}
	\spRange{90 feet}
	\spComponents{V, S, M (a small, straight piece of iron)}
	\spDuration{Concentration, up to 1 minute}
}
Choose a creature that you can see within range. The target must succeed on a Wisdom saving throw or be paralyzed for the duration. This spell has no effect on undead. At the end of each of its turns, the target can make another Wisdom saving throw. On a success, the spell ends on the target.
At Higher Levels. When you cast this spell using a spell slot of 6th level or higher, you can target one additional creature for each slot level above 5th. The creatures must be within 30 feet of each other when you target them.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of 6th level or higher, you can target one additional creature for each slot level above 5th. The creatures must be within 30 feet of each other when you target them.
\end{spell}

\begin{spell}{Legend Lore}{PHB}{5th-level divination}
{
	\spTime{10 minutes}
	\spRange{Self}
	\spComponents{V, S, M (incense worth at least 250 gp, which the spell consumes, and four ivory strips worth at least 50 gp each)}
	\spDuration{Instantaneous}
}
Name or describe a person, place, or object. The spell brings to your mind a brief summary of the significant lore about the thing you named. The lore might consist of current tales, forgotten stories, or even secret lore that has never been widely known. If the thing you named isn’t of legendary importance, you gain no information. The more information you already have about the thing, the more precise and detailed the information you receive is.
The information you learn is accurate but might be couched in figurative language. For example, if you have a mysterious magic axe on hand, the spell might yield this information: Woe to the evildoer whose hand touches the axe, for even the haft slices the hand of the evil ones. Only a true Child of Stone, lover and beloved of Moradin, may awaken the true powers of the axe, and only with the sacred word Rudnogg on the lips.
Spell Lists. Bard, Cleric, Wizard
\end{spell}

\begin{spell}{Mass Cure Wounds}{PHB}{5th-level evocation}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
A wave of healing energy washes out from a point of your choice within range. Choose up to six creatures in a 30-foot-radius sphere centered on that point. Each target regains hit points equal to 3d8 + your spellcasting ability modifier. This spell has no effect on undead or constructs.
At Higher Levels. When you cast this spell using a spell slot of 6th level or higher, the healing increases by 1d8 for each slot level above 5th.
Spell Lists. Bard, Cleric, Druid

\note{At Higher Levels.} When you cast this spell using a spell slot of 6th level or higher, the healing increases by 1d8 for each slot level above 5th.
\end{spell}

\begin{spell}{Mislead}{PHB}{5th-level illusion}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{S}
	\spDuration{Concentration, up to 1 hour}
}
You become invisible at the same time that an illusory double of you appears where you are standing. The double lasts for the duration, but the invisibility ends if you attack or cast a spell.
You can use your action to move your illusory double up to twice your speed and make it gesture, speak, and behave in whatever way you choose.
You can see through its eyes and hear through its ears as if you were located where it is. On each of your turns as a bonus action, you can switch from using its senses to using your own, or back again. While you are using its senses, you are blinded and deafened in regard to your own surroundings.
Spell Lists. Bard, Warlock (Optional), Wizard
\end{spell}

\begin{spell}{Modify Memory}{PHB}{5th-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
You attempt to reshape another creature’s memories. One creature that you can see must make a Wisdom saving throw. If you are fighting the creature, it has advantage on the saving throw. On a failed save, the target becomes charmed by you for the duration. The charmed target is incapacitated and unaware of its surroundings, though it can still hear you. If it takes any damage or is targeted by another spell, this spell ends, and none of the target’s memories are modified.
While this charm lasts, you can affect the target’s memory of an event that it experienced within the last 24 hours and that lasted no more than 10 minutes. You can permanently eliminate all memory of the event, allow the target to recall the event with perfect clarity and exacting detail, change its memory of the details of the event, or create a memory of some other event.
You must speak to the target to describe how its memories are affected, and it must be able to understand your language for the modified memories to take root. Its mind fills in any gaps in the details of your description. If the spell ends before you have finished describing the modified memories, the creature’s memory isn’t altered. Otherwise, the modified memories take hold when the spell ends.
A modified memory doesn’t necessarily affect how a creature behaves, particularly if the memory contradicts the creature’s natural inclinations, alignment, or beliefs. An illogical modified memory, such as implanting a memory of how much the creature enjoyed dousing itself in acid, is dismissed, perhaps as a bad dream. The DM might deem a modified memory too nonsensical to affect a creature in a significant manner.
A Remove Curse or Greater Restoration spell cast on the target restores the creature’s true memory.
At Higher Levels. If you cast this spell using a spell slot of 6th level or higher, you can alter the target’s memories of an event that took place up to 7 days ago (6th level), 30 days ago (7th level), 1 year ago (8th level), or any time in the creature’s past (9th level).
Spell Lists. Bard, Wizard

\note{At Higher Levels.} If you cast this spell using a spell slot of 6th level or higher, you can alter the target’s memories of an event that took place up to 7 days ago (6th level), 30 days ago (7th level), 1 year ago (8th level), or any time in the creature’s past (9th level).
\end{spell}

\begin{spell}{Planar Binding}{PHB}{5th-level abjuration}
{
	\spTime{1 hour}
	\spRange{60 feet}
	\spComponents{V, S, M (a jewel worth at least 1,000 gp, which the spell consumes)}
	\spDuration{24 hours}
}
With this spell, you attempt to bind a celestial, an elemental, a fey, or a fiend to your service. The creature must be within range for the entire casting of the spell. (Typically, the creature is first summoned into the center of an inverted Magic Circle in order to keep it trapped while this spell is cast.) At the completion of the casting, the target must make a Charisma saving throw. On a failed save, it is bound to serve you for the duration. If the creature was summoned or created by another spell, that spell’s duration is extended to match the duration of this spell.
A bound creature must follow your instructions to the best of its ability. You might command the creature to accompany you on an adventure, to guard a location, or to deliver a message. The creature obeys the letter of your instructions, but if the creature is hostile to you, it strives to twist your words to achieve its own objectives. If the creature carries out your instructions completely before the spell ends, it travels to you to report this fact if you are on the same plane of existence. If you are on a different plane of existence, it returns to the place where you bound it and remains there until the spell ends.
At Higher Levels. When you cast this spell using a spell slot of a higher level, the duration increases to 10 days with a 6th-level slot, 30 days with a 7th-level slot, 180 days with an 8th-level slot, or 1 year and 1 day with a 9th-level spell slot.
Spell Lists. Bard, Cleric, Druid, Warlock (Optional), Wizard

\note{At Higher Levels.} When you cast this spell using a spell slot of a higher level, the duration increases to 10 days with a 6th-level slot, 30 days with a 7th-level slot, 180 days with an 8th-level slot, or 1 year and 1 day with a 9th-level spell slot.
\end{spell}

\begin{spell}{Raise Dead}{PHB}{5th-level necromancy}
{
	\spTime{1 hour}
	\spRange{Touch}
	\spComponents{V, S, M (a diamond worth at least 500 gp, which the spell consumes)}
	\spDuration{Instantaneous}
}
You return a dead creature you touch to life, provided that it has been dead no longer than 10 days. If the creature’s soul is both willing and at liberty to rejoin the body, the creature returns to life with 1 hit point.
This spell also neutralizes any poison and cures nonmagical diseases that affected the creature at the time it died. This spell doesn’t, however, remove magical diseases, curses, or similar effects; if these aren’t first removed prior to casting the spell, they take effect when the creature returns to life. The spell can’t return an undead creature to life.
This spell closes all mortal wounds, but it doesn’t restore missing body parts. If the creature is lacking body parts or organs integral for its survival – its head, for instance – the spell automatically fails.
Coming back from the dead is an ordeal. The target takes a -4 penalty to all attack rolls, saving throws, and ability checks. Every time the target finishes a long rest, the penalty is reduced by 1 until it disappears.
Spell Lists. Bard, Cleric, Paladin
\end{spell}

\begin{spell}{Rary's Telepathic Bond}{PHB}{5th-level divination (ritual)}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (pieces of eggshell from two different kinds of creatures)}
	\spDuration{1 hour}
}
You forge a telepathic link among up to eight willing creatures of your choice within range, psychically linking each creature to all the others for the duration. Creatures with Intelligence scores of 2 or less aren’t affected by this spell.
Until the spell ends, the targets can communicate telepathically through the bond whether or not they have a common language. The communication is possible over any distance, though it can’t extend to other planes of existence.
Spell Lists. Bard (Optional), Wizard
\end{spell}

\begin{spell}{Scrying}{PHB}{5th-level divination}
{
	\spTime{10 minutes}
	\spRange{Self}
	\spComponents{V, S, M (a focus worth at least 1,000 gp, such as a crystal ball, a silver mirror, or a font filled with holy water)}
	\spDuration{Concentration, up to 10 minutes}
}
You can see and hear a particular creature you choose that is on the same plane of existence as you. The target must make a Wisdom saving throw, which is modified by how well you know the target and the sort of physical connection you have to it. If a target knows you’re casting this spell, it can fail the saving throw voluntarily if it wants to be observed.
On a successful save, the target isn’t affected, and you can’t use this spell against it again for 24 hours.
On a failed save, the spell creates an invisible sensor within 10 feet of the target. You can see and hear through the sensor as if you were there. The sensor moves with the target, remaining within 10 feet of it for the duration. A creature that can see invisible objects sees the sensor as a luminous orb about the size of your fist.
Instead of targeting a creature, you can choose a location you have seen before as the target of this spell. When you do, the sensor appears at that location and doesn’t move.
Spell Lists. Bard, Cleric, Druid, Warlock, Wizard
\end{spell}

\begin{spell}{Seeming}{PHB}{5th-level illusion}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S}
	\spDuration{8 hours}
}
This spell allows you to change the appearance of any number of creatures that you can see within range. You give each target you choose a new, illusory appearance. An unwilling target can make a Charisma saving throw, and if it succeeds, it is unaffected by this spell.
The spell disguises physical appearances as well as clothing, armor, weapons, and equipment. You can make each creature seem 1 foot shorter or taller and appear thin, fat, or in-between. You can’t change a target’s body type, so you must choose a form that has the same basic arrangement of limbs. Otherwise, the extent of the illusion is up to you. The spell lasts for the duration, unless you use your action to dismiss it sooner.
The changes wrought by this spell fail to hold up to physical inspections. For example, if you use this spell to add a hat to a creature’s outfit, objects pass through the hat, and anyone who touches it would feel nothing or would feel the creature’s head and hair. If you use this spell to appear thinner then you are, the hand of someone who reaches out to touch you would bump into you while it was seemingly still in midair.
A creature can use its action to inspect a target and make an Intelligence (Investigation) check against your spell save DC. If it succeeds, it becomes aware that the target is disguised.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Skill Empowerment}{XGE}{5th-level transmutation}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 hour}
}
Your magic deepens a creature’s understanding of its own talent. You touch one willing creature and give it expertise in one skill of your choice; until the spell ends, the creature doubles its proficiency bonus for ability checks it makes that use the chosen skill.
You must choose a skill in which the target is proficient and that isn’t already benefiting from an effect, such as Expertise, that doubles its proficiency bonus.
Spell Lists. Bard, Sorcerer, Wizard, Artificer
\end{spell}

\begin{spell}{Synaptic Static}{XGE}{5th-level enchantment}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
You choose a point within range and cause psychic energy to explode there. Each creature in a 20-foot-radius sphere centered on that point must make an Intelligence saving throw. A creature with an Intelligence score of 2 or lower can’t be affected by this spell. A target takes 8d6 psychic damage on a failed save, or half as much damage on a successful one.
After a failed save, a target has muddled thoughts for 1 minute. During that time, it rolls a d6 and subtracts the number rolled from all its attack rolls and ability checks, as well as its Constitution saving throws to maintain concentration. The target can make an Intelligence saving throw at the end of each of its turns, ending the effect on itself on a success.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Teleportation Circle}{PHB}{5th-level conjuration}
{
	\spTime{1 minute}
	\spRange{10 feet}
	\spComponents{V, M (rare chalks and inks infused with precious gems worth 50 gp, which the spell consumes)}
	\spDuration{1 round}
}
As you cast the spell, you draw a 10-foot-diameter circle on the ground inscribed with sigils that link your location to a permanent teleportation circle of your choice whose sigil sequence you know and that is on the same plane of existence as you.
A shimmering portal opens within the circle you drew and remains open until the end of your next turn. Any creature that enters the portal instantly appears within 5 feet of the destination circle or in the nearest unoccupied space if that space is occupied.
Many major temples, guilds, and other important places have permanent teleportation circles inscribed somewhere within their confines. Each such circle includes a unique sigil sequence – a string of magical runes arranged in a particular pattern. When you first gain the ability to cast this spell, you learn the sigil sequences for two destinations on the Material Plane, determined by the DM. You can learn additional sigil sequences during your adventures. You can commit a new sigil sequence to memory after studying it for 1 minute.
You can create a permanent teleportation circle by casting this spell in the same location every day for one year. You need not use the circle to teleport when you cast the spell in this way.
Spell Lists. Bard, Sorcerer, Warlock (Optional), Wizard
\end{spell}

