\begin{spell}{Eyebite}{PHB}{6th-level necromancy}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 minute}
}
For the spell’s duration, your eyes become an inky void imbued with dread power. One creature of your choice within 60 feet of you that you can see must succeed on a Wisdom saving throw or be affected by one of the following effects of your choice for the duration. On each of your turns until the spell ends, you can use your action to target another creature but can’t target a creature again if it has succeeded on a saving throw against this casting of eyebite.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Find the Path}{PHB}{6th-level divination}
{
	\spTime{1 minute}
	\spRange{Self}
	\spComponents{V, S, M (a set of divinatory tools – such as bones, ivory sticks, cards, teeth, or carved runes – worth 100 gp, and an object from the location you wish to find)}
	\spDuration{Concentration, up to 1 day}
}
This spell allows you to find the shortest, most direct physical route to a specific fixed location that you are familiar with on the same plane of existence. If you name a destination on another plane of existence, a destination that moves (such as a mobile fortress), or a destination that isn’t specific (such as "a green dragon’s lair”), the spell fails.
For the duration, as long as you are on the same plane of existence as the destination, you know how far it is and in what direction it lies. While you are traveling there, whenever you are presented with a choice of paths along the way, you automatically determine which path is the shortest and most direct route (but not necessarily the safest route) to the destination.
Spell Lists. Bard, Cleric, Druid
\end{spell}

\begin{spell}{Guards and Wards}{PHB}{6th-level abjuration}
{
	\spTime{10 minutes}
	\spRange{Touch}
	\spComponents{V, S, M (burning incense, a small measure of brimstone and oil, a knotted string, a small amount of umber hulk blood, and a small silver rod worth at least 10 gp)}
	\spDuration{24 hours}
}
You create a ward that protects up to 2,500 square feet of floor space (an area 50 feet square, or one hundred 5-foot squares or twenty-five 10-foot squares). The warded area can be up to 20 feet tall, and shaped as you desire. You can ward several stories of a stronghold by dividing the area among them, as long as you can walk into each contiguous area while you are casting the spell.
When you cast this spell, you can specify individuals that are unaffected by any or all of the effects that you choose. You can also specify a password that, when spoken aloud, makes the speaker immune to these effects.
Guards and Wards creates the following effects within the warded area.
The whole warded area radiates magic. A Dispel Magic cast on a specific effect, if successful, removes only that effect. You can create a permanently Guarded and Warded structure by casting this spell there every day for one year.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{Heroes' Feast}{PHB}{6th-level conjuration}
{
	\spTime{10 minutes}
	\spRange{30 feet}
	\spComponents{V, S, M (a gem-encrusted bowl worth at least 1,000 gp, which the spell consumes)}
	\spDuration{Instantaneous}
}
You bring forth a great feast, including magnificent food and drink. The feast takes 1 hour to consume and disappears at the end of that time, and the beneficial effects don’t set in until this hour is over. Up to twelve creatures can partake of the feast.
A creature that partakes of the feast gains several benefits. The creature is cured of all diseases and poison, becomes immune to poison and being frightened, and makes all Wisdom saving throws with advantage. Its hit point maximum also increases by 2d10, and it gains the same number of hit points. These benefits last for 24 hours.
Spell Lists. Bard (Optional), Cleric, Druid
\end{spell}

\begin{spell}{Mass Suggestion}{PHB}{6th-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, M (a snake’s tongue and either a bit of honeycomb or a drop of sweet oil)}
	\spDuration{24 hours}
}
You suggest a course of activity (limited to a sentence or two) and magically influence up to twelve creatures of your choice that you can see within range and that can hear and understand you. Creatures that can’t be charmed are immune to this effect. The suggestion must be worded in such a manner as to make the course of action sound reasonable. Asking the creature to stab itself, throw itself onto a spear, immolate itself, or do some other obviously harmful act automatically negates the effect of the spell.
Each target must make a Wisdom saving throw. On a failed save, it pursues the course of action you described to the best of its ability. The suggested course of action can continue for the entire duration. If the suggested activity can be completed in a shorter time, the spell ends when the subject finishes what it was asked to do.
You can also specify conditions that will trigger a special activity during the duration. For example, you might suggest that a group of soldiers give all their money to the first beggar they meet. If the condition isn’t met before the spell ends, the activity isn’t performed.
If you or any of your companions damage a creature affected by this spell, the spell ends for that creature.
At Higher Levels. When you cast this spell using a 7th-level spell slot, the duration is 10 days. When you use an 8th-level spell slot, the duration is 30 days. When you use a 9th-level spell slot, the duration is a year and a day.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell using a 7th-level spell slot, the duration is 10 days. When you use an 8th-level spell slot, the duration is 30 days. When you use a 9th-level spell slot, the duration is a year and a day.
\end{spell}

\begin{spell}{Otto's Irresistible Dance}{PHB}{6th-level enchantment}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V}
	\spDuration{Concentration, up to 1 minute}
}
Choose one creature that you can see within range. The target begins a comic dance in place: shuffling, tapping its feet, and capering for the duration. Creatures that can’t be charmed are immune to this spell.
A dancing creature must use all its movement to dance without leaving its space and has disadvantage on Dexterity saving throws and attack rolls. While the target is affected by this spell, other creatures have advantage on attack rolls against it. As an action, a dancing creature makes a Wisdom saving throw to regain control of itself. On a successful save, the spell ends.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{Programmed Illusion}{PHB}{6th-level illusion}
{
	\spTime{1 action}
	\spRange{120 feet}
	\spComponents{V, S, M (a bit of fleece and jade dust worth at least 25 gp)}
	\spDuration{Until dispelled}
}
You create an illusion of an object, a creature, or some other visible phenomenon within range that activates when a specific condition occurs. The illusion is imperceptible until then. It must be no larger than a 30-foot cube, and you decide when you cast the spell how the illusion behaves and what sounds it makes. This scripted performance can last up to 5 minutes.
When the condition you specify occurs, the illusion springs into existence and performs in the manner you described. Once the illusion finishes performing, it disappears and remains dormant for 10 minutes. After this time, the illusion can be activated again.
The triggering condition can be as general or as detailed as you like, though it must be based on visual or audible conditions that occur within 30 feet of the area. For example, you could create an illusion of yourself to appear and warn off others who attempt to open a trapped door, or you could set the illusion to trigger only when a creature says the correct word or phrase.
Physical interaction with the image reveals it to be an illusion, because things can pass through it. A creature that uses its action to examine the image can determine that it is an illusion with a successful Intelligence (Investigation) check against your spell save DC. If a creature discerns the illusion for what it is, the creature can see through the image, and any noise it makes sounds hollow to the creature.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{True Seeing}{PHB}{6th-level divination}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S, M (an ointment for the eyes that costs 25 gp; is made from mushroom powder, saffron, and fat; and is consumed by the spell)}
	\spDuration{1 hour}
}
This spell gives the willing creature you touch the ability to see things as they actually are. For the duration, the creature has truesight, notices secret doors hidden by magic, and can see into the Ethereal Plane, all out to a range of 120 feet.
Spell Lists. Bard, Cleric, Sorcerer, Warlock, Wizard
\end{spell}

