\begin{spell}{Antipathy/Sympathy}{PHB}{8th-level enchantment}
{
	\spTime{1 hour}
	\spRange{60 feet}
	\spComponents{V, S, M (either a lump of alum soaked in vinegar for the antipathy effect or a drop of honey for the sympathy effect)}
	\spDuration{10 days}
}
This spell attracts or repels creatures of your choice. You target something within range, either a Huge or smaller object or creature or an area that is no larger than a 200-foot cube. Then specify a kind of intelligent creature, such as red dragons, goblins, or vampires. You invest the target with an aura that either attracts or repels the specified creatures for the duration. Choose antipathy or sympathy as the aura’s effect.
Spell Lists. Bard (Optional), Druid, Wizard
\end{spell}

\begin{spell}{Dominate Monster}{PHB}{8th-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Concentration, up to 1 hour}
}
You attempt to beguile a creature that you can see within range. It must succeed on a Wisdom saving throw or be charmed by you for the duration. If you or creatures that are friendly to you are fighting it, it has advantage on the saving throw.
While the creature is charmed, you have a telepathic link with it as long as the two of you are on the same plane of existence. You can use this telepathic link to issue commands to the creature while you are conscious (no action required), which it does its best to obey. You can specify a simple and general course of action, such as "Attack that creature," "Run over there," or "Fetch that object." If the creature completes the order and doesn’t receive further direction from you, it defends and preserves itself to the best of its ability.
You can use your action to take total and precise control of the target. Until the end of your next turn, the creature takes only the actions you choose, and doesn’t do anything that you don’t allow it to do. During this time, you can also cause the creature to use a reaction, but this requires you to use your own reaction as well.
Each time the target takes damage, it makes a new Wisdom saving throw against the spell. If the saving throw succeeds, the spell ends.
At Higher Levels. When you cast this spell with a 9th-level spell slot, the duration is concentration, up to 8 hours.
Spell Lists. Bard, Sorcerer, Warlock, Wizard

\note{At Higher Levels.} When you cast this spell with a 9th-level spell slot, the duration is concentration, up to 8 hours.
\end{spell}

\begin{spell}{Feeblemind}{PHB}{8th-level enchantment}
{
	\spTime{1 action}
	\spRange{150 feet}
	\spComponents{V, S, M (a handful of clay, crystal, glass, or mineral spheres)}
	\spDuration{Instantaneous}
}
You blast the mind of a creature that you can see within range, attempting to shatter its intellect and personality. The target takes 4d6 psychic damage and must make an Intelligence saving throw.
On a failed save, the creature’s Intelligence and Charisma scores become 1. The creature can’t cast spells, activate magic items, understand language, or communicate in any intelligible way. The creature can, however, identify its friends, follow them, and even protect them.
At the end of every 30 days, the creature can repeat its saving throw against this spell. If it succeeds on its saving throw, the spell ends. The spell can also be ended by Greater Restoration, Heal, or Wish.
Spell Lists. Bard, Druid, Warlock, Wizard
\end{spell}

\begin{spell}{Glibness}{PHB}{8th-level transmutation}
{
	\spTime{1 action}
	\spRange{Self}
	\spComponents{V}
	\spDuration{1 hour}
}
Until the spell ends, when you make a Charisma check, you can replace the number you roll with a 15. Additionally, no matter what you say, magic that would determine if you are telling the truth indicates that you are being truthful.
Spell Lists. Bard, Warlock
\end{spell}

\begin{spell}{Mind Blank}{PHB}{8th-level abjuration}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{24 hours}
}
Until the spell ends, one willing creature you touch is immune to psychic damage, any effect that would sense its emotions or read its thoughts, divination spells, and the charmed condition. The spell even foils wish spells and spells or effects of similar power used to affect the target's mind or to gain information about the target.
Spell Lists. Bard, Wizard
\end{spell}

\begin{spell}{Power Word: Stun}{PHB}{8th-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
You speak a word of power that can overwhelm the mind of one creature you can see within range, leaving it dumbfounded. If the target has 150 hit points or fewer, it is stunned. Otherwise, the spell has no effect. The stunned target must make a Constitution saving throw at the end of each of its turns. On a successful save, this stunning effect ends.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

