\begin{spell}{Foresight}{PHB}{9th-level divination}
{
	\spTime{1 minute}
	\spRange{Touch}
	\spComponents{V, S, M (a hummingbird feather)}
	\spDuration{8 hours}
}
You touch a willing creature and bestow a limited ability to see into the immediate future. For the duration, the target can’t be surprised and has advantage on attack rolls, ability checks, and saving throws. Additionally, other creatures have disadvantage on attack rolls against the target for the duration. This spell immediately ends if you cast it again before its duration ends.
Spell Lists. Bard, Druid, Warlock, Wizard
\end{spell}

\begin{spell}{Mass Polymorph}{XGE}{9th-level transmutation}
{
	\spTime{1 Action}
	\spRange{120 feet}
	\spComponents{V, S, M (a caterpillar cocoon)}
	\spDuration{Concentration, up to 1 hour}
}
You transform up to ten creatures of your choice that you can see within range. An unwilling target must succeed on a Wisdom saving throw to resist the transformation. An unwilling shapechanger automatically succeeds on the save.
Each target assumes a beast form of your choice, and you can choose the same form or different ones for each target. The new form can be any beast you have seen whose challenge rating is equal to or less than the target’s (or half the target’s level, if the target doesn’t have a challenge rating). The target’s game statistics, including mental ability scores, are replaced by the statistics of the chosen beast, but the target retains its hit points, alignment, and personality.
Each target gains a number of temporary hit points equal to the hit points of its new form. These temporary hit points can’t be replaced by temporary hit points from another source. A target reverts to its normal form when it has no more temporary hit points or it dies. If the spell ends before then, the creature loses all its temporary hit points and reverts to its normal form.
The creature is limited in the actions it can perform by the nature of its new form. It can’t speak, cast spells, or do anything else that requires hands or speech. The target’s gear melds into the new form.
The target can’t activate, use, wield, or otherwise benefit from any of its equipment.
Spell Lists. Bard, Sorcerer, Wizard
\end{spell}

\begin{spell}{Power Word: Heal}{PHB}{9th-level evocation}
{
	\spTime{1 action}
	\spRange{Touch}
	\spComponents{V, S}
	\spDuration{Instantaneous}
}
A wave of healing energy washes over a creature you touch. The target regains all its hit points. If the creature is charmed, frightened, paralyzed, or stunned, the condition ends. If the creature is prone, it can use its reaction to stand up. This spell has no effect on undead or constructs.
Spell Lists. Bard, Cleric (Optional)
\end{spell}

\begin{spell}{Power Word: Kill}{PHB}{9th-level enchantment}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V}
	\spDuration{Instantaneous}
}
You utter a word of power that can compel one creature you can see within range to die instantly. If the creature you chose has 100 hit points or fewer, it dies. Otherwise, the spell has no effect.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{Prismatic Wall}{PHB}{9th-level abjuration}
{
	\spTime{1 action}
	\spRange{60 feet}
	\spComponents{V, S}
	\spDuration{10 minutes}
}
A shimmering, multicolored plane of light forms a vertical opaque wall – up to 90 feet long, 30 feet high, and 1 inch thick – centered on a point you can see within range. Alternatively, you can shape the wall into a sphere up to 30 feet in diameter centered on a point you choose within range. The wall remains in place for the duration. If you position the wall so that it passes through a space occupied by a creature, the spell fails, and your action and the spell slot are wasted.
The wall sheds bright light out to a range of 100 feet and dim light for an additional 100 feet. You and creatures you designate at the time you cast the spell can pass through and remain near the wall without harm. If another creature that can see the wall moves to within 20 feet of it or starts its turn there, the creature must succeed on a Constitution saving throw or become blinded for 1 minute.
The wall consists of seven layers, each with a different color. When a creature attempts to reach into or pass through the wall, it does so one layer at a time through all the wall’s layers. As it passes or reaches through each layer, the creature must make a Dexterity saving throw or be affected by that layer’s properties as described below.
The wall can be destroyed, also one layer at a time, in order from red to violet, by means specific to each layer. Once a layer is destroyed, it remains so for the duration of the spell. An Antimagic Field has no effect on it.
Spell Lists. Bard (Optional), Wizard
\end{spell}

\begin{spell}{Psychic Scream}{XGE}{9th-level enchantment}
{
	\spTime{1 action}
	\spRange{90 feet}
	\spComponents{S}
	\spDuration{Instantaneous}
}
You unleash the power of your mind to blast the intellect of up to ten creatures of your choice that you can see within range. Creatures that have an Intelligence score of 2 or lower are unaffected.
Each target must make an Intelligence saving throw. On a failed save, a target takes 14d6 psychic damage and is stunned. On a successful save, a target takes half as much damage and isn’t stunned. If a target is killed by this damage, its head explodes, assuming it has one.
A stunned target can make an Intelligence saving throw at the end of each of its turns. On a successful save, the stunning effect ends.
Spell Lists. Bard, Sorcerer, Warlock, Wizard
\end{spell}

\begin{spell}{True Polymorph}{PHB}{9th-level transmutation}
{
	\spTime{1 action}
	\spRange{30 feet}
	\spComponents{V, S, M (a drop of mercury, a dollop of gum arabic, and a wisp of smoke)}
	\spDuration{Concentration, up to 1 hour}
}
Choose one creature or nonmagical object that you can see within range. You transform the creature into a different creature, the creature into a nonmagical object, or the object into a creature (the object must be neither worn nor carried by another creature). The transformation lasts for the duration, or until the target drops to 0 hit points or dies. If you concentrate on this spell for the full duration, the transformation becomes permanent.
Shapechangers aren't affected by this spell. An unwilling creature can make a Wisdom saving throw, and if it succeeds, it isn't affected by this spell.
This spell can't affect a target that has 0 hit points.
Spell Lists. Bard, Warlock, Wizard
\end{spell}

